### 2017-07-26 paper/evaluation.tex
Addressed reviewer 1's comments about C* configs

It is worth mentioning that we used JUnit as opposed to Maven to run
configurations \emph{C*}.  After carefully verifying library versions
for compatibility issues and comparing results with JUnit's we
observed that several of Maven's executions exposed problems.  For
example, Maven incorrectly counts the number of test cases executed
for some cases where test flakiness are observed.  These issues are
categorized and documented on our website~\cite{ourwebpage} with
Docker containers (for reproduction).  To address those issues we
implemented basic JUnit test runners (one for each \emph{C*}
configuration), reflecting the effects of parallel configurations from
Maven Surefire.  To write those runners we used Maven log files to
identify test classes to run and used the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we invoke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
insignificant differences (a fraction of seconds in most cases).  To
assure that our experiments terminate (recall that deadlock or livelock
could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
configured to dispatch a \emph{kill} signal if test execution exceeds
a given time limit. Finally, we saved each execution log and stack
traces generated from JUnit to collect the execution time,
the number of failing tests, and for reference to analyze and diagnose
outliers in our results.

>>>>

It is worth mentioning that we used \Jbc{custom} JUnit \Jbc{runners}
as opposed to Maven to run \Comment{configurations \emph{C*}}test
suites with different parallel configurations (see
Section~\ref{sec:modes})\Jbc{$\leftarrow$ Reviewer 1 was confused with
the notation \emph{C*} AND the original sentence was not accurate to
this paragraph}.
After carefully verifying library versions
for compatibility issues and comparing results with JUnit's we
observed that several of Maven's executions exposed problems.  For
example, Maven incorrectly counts the number of test cases executed
for some cases where test flakiness are observed.  These issues are
categorized and documented on our website~\cite{ourwebpage} with
Docker containers (for reproduction).  To address those issues we
implemented basic JUnit test runners (one for each \Jbc{parallel}
configuration), reflecting the effects of parallel configurations from
Maven Surefire.  To write those runners we used Maven log files to
identify test classes to run and used the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we invoke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
insignificant differences (a fraction of seconds in most cases).  To
assure that our experiments terminate (recall that deadlock or livelock
could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
configured to dispatch a \emph{kill} signal if test execution exceeds
a given time limit. Finally, we saved each execution log and stack
traces generated from JUnit to collect the execution time,
the number of failing tests, and for reference to analyze and diagnose
outliers in our results.
